Testing Charts: viewers' perceptual accuracy in surveys

### 2023-07-20 SDSS-2023/testing-charts-accuracy.qmd
oops - commenting out some notes

Results to discuss:

There are differences by alignment
There are not huge differences across structures
However, we see a difference in how people react across different structures (zooming behavior, certainty? time?)

- We can reproduce prior findings with nat rep sample 
- We can rank 
- We can rank better because we have a bigger sample size 
- We can find changes in viewer behavior 
- Demographics matter to accuracy and choices

@@

-   Other important measures beyond accuracy: time to completion (automatic on web), certainty in response (asked).

-   Studying how viewers interact with charts can be done in a survey, and more expansive work on this topic should be completed to understand how the general public interacts with and understands charts.

    -   Design choices impact viewer behavior: zooming

-   (some) Demographics matter: age and gender does not seem to matter for perception economic background and education does matter for perception: we need to know, we do not want to create a hurdle in communication

>>>>

<!-- Results to discuss: -->

<!-- There are differences by alignment -->
<!-- There are not huge differences across structures -->
<!-- However, we see a difference in how people react across different structures (zooming behavior, certainty? time?) -->

<!-- - We can reproduce prior findings with nat rep sample  -->
<!-- - We can rank  -->
<!-- - We can rank better because we have a bigger sample size  -->
<!-- - We can find changes in viewer behavior  -->
<!-- - Demographics matter to accuracy and choices -->

@@

<!-- -   Other important measures beyond accuracy: time to completion (automatic on web), certainty in response (asked). -->

<!-- -   Studying how viewers interact with charts can be done in a survey, and more expansive work on this topic should be completed to understand how the general public interacts with and understands charts. -->

<!--     -   Design choices impact viewer behavior: zooming -->

<!-- -   (some) Demographics matter: age and gender does not seem to matter for perception economic background and education does matter for perception: we need to know, we do not want to create a hurdle in communication -->
